\documentclass[12pt]{article}
%
\usepackage{amssymb,amsmath,cite}

\setlength{\textheight}{23cm}
\setlength{\textwidth}{16cm}
\setlength{\topmargin}{0cm}
\setlength{\headheight}{0pt}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
%\setlength{\unitlength}{0.7mm}
%
\def\nn{\nonumber}

\newtheorem{lemma}{Lemma}%[section]
\newtheorem{prop}[lemma]{Proposition}
%\newtheorem{thm}[lemma]{Theorem}
\newtheorem{thm}{Theorem}
\newtheorem{cor}[lemma]{Corollary}
\newtheorem{defo}{Definition}
%
%
%
\begin{document}

\begin{center}
{\large\bf Reduced Wigner coefficients for unitary representations
of the Lie superalgebra $gl(m|n)$}\\
~~\\

{\large Jason L. Werry, Phillip S. Isaac and Mark D. Gould}\\
~~\\

School of Mathematics and Physics, The University of Queensland, St Lucia QLD 4072, Australia.
\end{center}

\begin{abstract}
In this paper fundamental Wigner coefficients are determined
algebraically by considering the eigenvalues of certain generalized Casimir invariants. Here this
method is applied in the context of both type 1 and type 2 unitary representations of the Lie superalgebra $gl(m|n)$.
\end{abstract}

% \begin{flushright}
% May 9, 2012
% \end{flushright}
% 
% \begin{tableofcontents}
% \end{tableofcontents}

\section{Introduction}
The application of the theory of Lie Superalgebras to problems in mathematical physics relies on the construction of an explicit set of basis states of an irreducible representation and also the explicit
determination of Wigner (Clebsch-Gordan) coefficients. Prior to the development of Lie superalgerbra theory, the foundational papers by Gel'fand and Tsetlin \cite{GT1950,GT1950b} gave a novel construction of basis vectors for the irreducible representations of the unitary and orthogonal groups. Further work by Baird and Biedenharn \cite{BB1963} gave a proof of Gel'fand and Tsetlin's results while also giving , for the first time, both the fundamental and reduced Wigner coefficients for the Lie group U(n). In the same paper, the factorization of a matrix element into a Wigner coefficient and a reduced matrix element was also examined.

The utility of the characteristic identities (polynomial identities satisfied by generators of the Lie algebra) towards these goals became apparent during the 1970s and 80s and resulted in the algebraic determination of reduced matrix elements, \cite{Gould1978} raising and lowering generators \cite{Gould1980} and matrix elements, \cite{Gould1981,Gould1981b}. In the papers \cite{GIW2,GIW3} the matrix elements of unitary representations of $gl(m|n)$ were given explicitly using similar techniques. The resulting closed-form expressions were obtained by utilizing the factorization of a matrix element into a Wigner coefficient and a reduced matrix element. The vector Wigner coefficients thus obtained allow us in this paper to obtain all fundamental $gl(m|n)$ Wigner coefficients (WCs) in the Gelfand-Tsetlin (GT) basis for both type 1 and type 2 unitary representations. Although the resulting expressions for these Reduced Wigner coefficients have appeared in \cite{StoiVan2010}, in this presentation we obtain our results from first principles using algebraic methods that can be directly generalised to other Lie algebras as well as the quantum case.
 
%A summary of the background regarding the characteristic identities and their associated invariants in Section \ref{prelim}. We then continue by introducing the Wigner coefficients in Section \ref{Wigner} and give their expressions in terms of representation labels of the representation concerned. Finally, Section 4 concludes with a discussion of these results.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Characteristic identities and associated invariants}
\label{prelim}

We utilise the notation used in the series \cite{GIW1,GIW2,GIW3}. The generators of the Lie superalgebra $gl(m|n)$ are denoted $E_{ij}$ where $1 \leq p,q \leq m+n$. The values $1 \leq i,j \leq m$ are called \textit{even} while the values $m < i,j \leq m+n$ are called \textit{odd}.

The graded index notation will be used where the Latin indices $i,j,...$ are used for even quantities and the Greek indices $\mu, \nu, ...$ for odd quantities. The grading operator $(~)$ will then give
$$
(i) = 0,~(\mu) = 1
$$
and then set of generators is then given by 
$$
E_{ij}, E_{i\mu}, E_{\mu i}, E_{\mu\nu}.
$$
We reserve the indices $p,q$ to be ungraded and to range fully from $1$ to $m+n$.

A weight $\Lambda$ may be expanded in terms
of the elementary weights $\varepsilon_p$ ($1\leq p\leq m+n$) so that
\begin{equation*}
\Lambda = \sum_{p=1}^m\Lambda_p\varepsilon_p 
\end{equation*}
where $\epsilon_p$ is the $m+n$-tuple with $1$ in position $p$ and zeros elsewhere.

The adjoint tensor operator $\bar{\mathcal{A}}$ constructed in \cite{GIW1} plays an important role in what follows and is defined as the $m+n$ square matrix with entries
$$
\bar{\mathcal{A}}_{pq} = -(-1)^{(p)(q)} E_{qp}.
$$
When $\bar{\mathcal{A}}$ acts on an irreducible type 1 unitary $gl(m|n)$ module $V(\Lambda)$ of highest weight $\Lambda$ it will satisfy the characteristic identity
\begin{align}
\prod_{i=1}^m ({\cal \bar{A}} - \bar{\alpha}_i) \prod^n_{\mu = 1} ({\cal \bar{A}} - \bar{\alpha}_\mu) = 0
\label{CharIdent1}
\end{align}
where the adjoint roots $\bar{\alpha}_i, \bar{\alpha}_\mu$ are given in terms of the highest weight labels
$$
\Lambda = (\Lambda_{i=1},...,\Lambda_{i=m}|\Lambda_{\mu=1},...\Lambda_{\mu=n})
$$
as
$$
{\bar{\alpha}}_i= i - 1 -\Lambda_i ,~~ {\bar{\alpha}}_\mu = \Lambda_\mu + m + 1 - \mu. 
$$
Immediately from the characteristic identity, we see that for each integer $r$ where $1 \leq  r \leq m+n$ there exist the projection operators 
%$$
%\bar{P}[r]: V(\varepsilon_1) \otimes V(\Lambda) \longrightarrow V(\Lambda + \epsilon_r)
%$$
%given by
\begin{align*}
\bar{P}[r] = \prod^{m+n}_{k \neq r} \left( \frac{{\cal \bar{A}} - \bar{\alpha}_k}{\bar{\alpha}_r
- \bar{\alpha}_k} \right)\nn.
\end{align*}
Similarly we have the vector matrix $\mathcal{A}$ with entries
$$
\mathcal{A}_{pq} = -(-1)^{(p)} E_{pq}.
$$
that satisfy the polynomial identities on an irreducible type 2 unitary $gl(m|n)$ module
\begin{align}
\prod_{i=1}^m ({\cal A} - \alpha_i) \prod^n_{\mu = 1} ({\cal A} - \alpha_\mu) = 0
\label{CharIdent2}
\end{align}
where
$$
{\alpha}_i= \Lambda_i + m - n - i ,~~ {\alpha}_\mu = \mu - \Lambda_\mu -n. 
$$
The associated projection operators 
%$$
%P[r]: V^*(\varepsilon_1) \otimes V(\Lambda) \longrightarrow V(\Lambda - \epsilon_r)
%$$
are then given by
\begin{align*}
P[r] = \prod^{m+n}_{k \neq r} \left( \frac{{\cal A} - \alpha_k}{\alpha_r
- \alpha_k} \right)\nn.
\end{align*}
%We will now apply the characteristic identities (\ref{CharIdent1}) and (\ref{CharIdent2}) to evaluate the operators
%\begin{align*}
%\bar{c}_r = \bar{P}[r]_{m+n}^{\ m+n}
%\end{align*}
%and 
%\begin{align*}
%c_r = P[r]_{\ m+n}^{m+n}
%\end{align*}
%which are essentially squares of reduced Wigner coefficients. This correspondence will be explained more fully in the next section. 

%We will now show that the eigenvalues of the invariants 
%\begin{align*}
%\bar{c}_r = \bar{P}[r]_{m+n}^{\ m+n}
%\end{align*}
%and 
%\begin{align*}
%c_r = P[r]_{\ m+n}^{m+n}
%\end{align*}
%are essentially squares of reduced Wigner coefficients. 

We now define the $gl(m|n-1)$ analogue of the matrix $\bar{\mathcal{A}}_{pq}$ so that we have the corresponding $(m+n-1) \times (m+n-1)$ square matrix
$$
\bar{\mathcal{A}_0}_{pq} = -(-1)^{(p)(q)} E_{qp}
$$
that satisfies the usual polynomial identities on an irreducible type 1 unitary module with highest weight $\lambda$:
\begin{align*}
\prod_{i=1}^m (\bar{\mathcal{A}_0} - \bar{\alpha_0}_i) \prod^{n+1}_{\mu = 1} (\bar{\mathcal{A}_0} - \bar{\alpha_0}_\mu) &= 0.
\end{align*}
Here the roots are given by
\begin{align*}
\bar{\alpha_0}_i  &= i - 1 -{\lambda}_i , &1\leq i\leq m, \\
\bar{\alpha_0}_\mu &= {\lambda}_\mu + m + 1 - \mu,  &1\leq \mu \leq n - 1,
\end{align*}
and the $gl(m|n-1)$ projection operators are given by
\begin{align}
\bar{P_0}[r] = \prod_{k\neq r}^{m+n+1}\left( \frac{\bar{\mathcal{A}_0}  -\bar{\alpha_0}_k}{\bar{\alpha_0}_r - \bar{\alpha_0}_k} \right).
\end{align}
The betweenness conditions imply 
\cite{GIW1}, for $1\leq i\leq m$, that we have only two cases
\begin{align}
\bar{\alpha}_i = \left\{ \begin{array}{rl}  \bar{\alpha_0}_i - 1,& \Lambda_i = 1+\lambda_i\\
                                    \bar{\alpha_0}_i,& \Lambda_i = \lambda_i  ~~.
\end{array} \right.
\nn
%\label{equ5.4} 
\end{align}
We therefore define the following index sets
\begin{align}
I_0 &=  \{ 1\leq i\leq m\ |\ \bar{\alpha_0}_i=1+\bar{\alpha}_i \},\nn\\
\bar{I}_0 &=  \{ 1\leq i\leq m\ |\ \bar{\alpha_0}_i=\bar{\alpha}_i  \},\nn\\
I_1 &= \{ 1\leq\mu\leq n-1\},\nn\\
I &= I_0\cup I_1,\nn\\
I'&= \bar{I}_0\cup I_1,\nn\\
\tilde{I} &= I\cup \{m+n\},\nn\\
\tilde{I}' &= I'\cup \{m+n\}.
\label{DefIndexSets1} 
\end{align}
The operators
\begin{align*}
\bar{c}_r = \bar{P}[r]_{m+n}^{\ m+n}
\end{align*}
are essentially squares of reduced Wigner coefficients and this correspondence will be explained more fully in the next section. By considering the characteristic identity (\ref{CharIdent1}) satisfied by the matrix $\bar{\mathcal{A}}$ we may obtain the invariant $\bar{c}_r$ as a rational polynomial in terms of the roots $\bar{\alpha}_i$ and $\bar{\alpha}_\mu$. Specifically, we have \cite{GIW1}
\begin{align}
\bar{c}_r = \prod_{k\in \tilde{I}',k\neq r} \left(\bar{\alpha}_r - \bar{\alpha}_k\right)^{-1}\prod_{k\in
I'} \left(\bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)}\right),\ \ r\in \tilde{I}',
\label{barseer}
\end{align}

Note that equation (\ref{barseer}) is positive as expected. The definition of the projection $\bar{P_0}[r]$ allows the calculation of the invariant $\bar{\rho}_{ru}$ in the following expressions \cite{GIW2}
\begin{align}
(\bar{P}_0[u]\bar{P}[r]\bar{P}_0[u])_p^{\ q} &= \bar{\rho}_{ru}\bar{P}_0[u]_p^{\ q}.
\end{align}
Explicitly, $\bar{\rho}_{ru}$ is the $gl(m|n-1)$ invariant operator given by
\begin{align}
\bar{\rho}_{ru} &= (\bar{\alpha}_r-\bar{\alpha_0}_u +
1)^{-1}(\bar{\alpha}_r-\bar{\alpha_0}_u)^{-1}\bar{c}_r\bar{\delta}_u, \ \ \ (u) = 1, \nn\\
\bar{\rho}_{ru} &= (\bar{\alpha}_r-\bar{\alpha_0}_u +
1)^{-1}(\bar{\alpha}_r-\bar{\alpha_0}_u)^{-1}\bar{c}_r\bar{\delta}_u \ \ \ (u) = 0, u \neq r,
\nn\\
\bar{\rho}_{uu} &= \bar{c}_u \bar{\delta}_u, \ \ \ (u) = 0, \nn\\
\bar{\rho}_{ru} &= (\bar{\alpha}_r-\bar{\alpha_0}_u -
1)^{-1}(\bar{\alpha}_r-\bar{\alpha_0}_u)^{-1}\bar{c}_r \bar{\delta}_u \ \ \ gl(m)
\hbox{~case,} 
\label{RhoBarExp}
\end{align}
%whose eigenvalues determine the square of $gl(m|n):gl(m|n-1)$ reduced vector Wigner
%coefficients via
%\begin{align}
%\bar{\rho}_{ru}  &= \left| \left\langle\left. 
%\begin{array}{c} \Lambda+\varepsilon_r\\ \lambda+\varepsilon_{0_u} \end{array}
%\right|\right.
%\left.
%\begin{array}{c} \varepsilon_1 \\
%\varepsilon_{0_1} \end{array} 
%;
% \begin{array}{c} \Lambda \\
%\lambda \end{array}
%\right\rangle \right|^2,
%\end{align}
%and where
where
\begin{align}
\bar{\delta}_u &= (-1)^{|I'|} \prod_{k\in I',k\neq u}\left(\bar{\alpha_0}_u - \bar{\alpha_0}_k -
(-1)^{(k)}\right)^{-1} \prod_{k\in \tilde{I}'}\left(\bar{\alpha}_k - \bar{\alpha_0}_u \right), u\in I, 
\end{align}
are the reduced matrix elements.
Note that $\bar{\rho}_{ru}$ in equation (\ref{RhoBarExp}) is non-vanishing only when $r\in \tilde{I}'$ and $u\in I$.

Substituting the expressions for $\bar{c}_r$ and $\bar{\delta}_u$ into equation 
 (\ref{RhoBarExp}) gives
\begin{align*}
\bar{\rho}_{ru} &= (\bar{\alpha}_r-\bar{\alpha_0}_u + 1)^{-1}\prod_{k\in \tilde{I'},k\neq r} \left(\bar{\alpha}_r - \bar{\alpha}_k \right)^{-1}\prod_{k\in
I'} \left(\bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)}\right) \\
& ~\times (-1)^{|I'|} \prod_{k\in I',k\neq u} \left(\bar{\alpha_0}_u - \bar{\alpha_0}_k -
(-1)^{(k)}\right)^{-1}\prod_{k\in\tilde{I'},k \neq r} \left(\bar{\alpha}_k - \bar{\alpha_0}_u \right),\ \ r\in \tilde{I'},u\in I 
\end{align*}
for $u$ even and
\begin{align*}
\bar{\rho}_{ru} &= (-1)^{|I'|} \prod_{k\in \tilde{I'},k\neq r} 
\left(
\frac 
{\bar{\alpha}_k - \bar{\alpha_0}_u  }
{\bar{\alpha}_r - \bar{\alpha}_k }
\right)
\prod_{k\in I',k \neq u} 
\left(
\frac
{ \bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)} }
{\bar{\alpha_0}_u - \bar{\alpha_0}_k - (-1)^{(k)} }
\right)
,\ \ r\in \tilde{I'},u\in I_1
\end{align*}
for $u$ odd. Note that the expressions for $\bar{\rho}_{ru}$ always evaluate to positive values as expected.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Similarly, the $gl(m|n-1)$ analogue of ${\mathcal{A}}_{pq}$ is the $(m+n-1) \times (m+n-1)$ square matrix
$$
{\mathcal{A}_0}_{pq} = -(-1)^{(p)} E_{pq}
$$
that satisfies the usual polynomial identities on an irreducible type 2 unitary module with highest weight $\lambda$ is
\begin{align*}
	\prod^m_{i=1} (\mathcal{A}_0 - {\alpha_0}_i ) \prod^{n+1}_{\mu=1} (\mathcal{A}_0 - {\alpha_0}_\mu) &= 0 .
\end{align*}
Here the roots are given by
\begin{align*}
{\alpha_0}_i &= {\lambda}_i + m - n + 1 - i, &1\leq i\leq m, \\
{\alpha_0}_\mu &= \mu-{\lambda}_\mu - n + 1, &1\leq \mu \leq n - 1 
\end{align*}
and the dual $gl(m|n-1)$ projection operators are expressed as
\begin{align}
P_0[r] = \prod_{k\neq r}^{m+n+1}\left( 
\frac{\mathcal{A}_0-{\alpha_0}_k}
{{\alpha_0}_r-{\alpha_0}_k} \right).
\end{align}
The betweenness conditions imply 
\cite{GIW3}, for $1\leq i\leq m$, that we have only two cases
\begin{align}
\alpha_i = \left\{ \begin{array}{rl} {\alpha_0}_i,& \Lambda_i = 1+\lambda_i\\
                                    {\alpha_0}_i - 1,& \Lambda_i = \lambda_i  ~~.
\end{array} \right.
\nn
%\label{equ5.4} 
\end{align}
The index sets in terms of the adjoint roots $\alpha_i$ and ${\alpha_0}_i$ are then
\begin{align}
I_0 &=  \{ 1\leq i\leq m\ |\ {\alpha_0}_i=\alpha_i\},\nn\\
\bar{I}_0 &=  \{ 1\leq i\leq m\ |\ {\alpha_0}_i=1+\alpha_i\},\nn\\
I_1 &= \{ 1\leq\mu\leq n-1\},\nn\\
I &= I_0\cup I_1,\nn\\
I'&= \bar{I}_0\cup I_1,\nn\\
\tilde{I} &= I\cup \{m+n\},\nn\\
\tilde{I}' &= I'\cup \{m+n\}.
\label{DefIndexSets2} 
\end{align}
Similarly, we define the analogue of the $\bar{c}_r$ operator 
\begin{align*}
c_r = P[r]_{\ m+n}^{m+n}
\end{align*}
which is also related to the squares of reduced Wigner coefficients.

By considering the characteristic identities satisfied by the matrix $\bar{\mathcal{A}}$ we may obtain the invariant $c_r$ as a rational polynomial in terms of the roots $\alpha_i,\alpha_\mu$ and ${\alpha_0}_i,{\alpha_0}_\mu$. Specifically, we have \cite{GIW1}
\begin{align}
c_r = \prod_{k\in \tilde{I},k\neq r} \left(\alpha_r - \alpha_k \right)^{-1}\prod_{k\in
I} \left(\alpha_r - {\alpha_0}_k - (-1)^{(k)}\right),\ \ r\in \tilde{I} ,
\label{seer}
\end{align}
and note that equation (\ref{seer}) is positive (as expected).

The definitions of the projections ${P_0}[r]$ and ${P}[r]$ allow the calculation of the invariant ${\rho}_{ru}$ in the following expressions \cite{GIW2}
\begin{align}
({P_0}[u]{P}[r]{P_0}[u])_p^{\ q} &= {\rho}_{ru}{P_0}[u]_{\ p}^q 
\end{align}
where ${\rho}_{ru}$ are the $gl(m|n-1)$ invariant operators given by
\begin{align}
{\rho}_{ru} &= ({\alpha}_r-{\alpha_0}_u +
1)^{-1}({\alpha}_r-{\alpha_0}_u)^{-1}{c}_r{\delta}_u, \ \ \ (u) = 1, \nn\\
{\rho}_{ru} &= ({\alpha}_r-{\alpha_0}_u +
1)^{-1}({\alpha}_r-{\alpha_0}_u)^{-1}{c}_r{\delta}_u \ \ \ (u) = 0, u \neq r,
\nn\\
{\rho}_{uu} &= {c}_u {\delta}_u, \ \ \ (u) = 0, \nn\\
{\rho}_{ru} &= ({\alpha}_r-{\alpha_0}_u -
1)^{-1}({\alpha}_r-{\alpha_0}_u)^{-1}{c}_r {\delta}_u \ \ \ gl(m)
\hbox{~case,} 
\label{RhoExp}
\end{align}
%whose eigenvalues determine the square of $gl(m|n):gl(m|n-1)$ reduced dual vector Wigner
%coefficients via
%\begin{align}
%\rho_{ru} &= \left| \left\langle\left. 
%\begin{array}{c} \Lambda-\varepsilon_r\\ \lambda-\varepsilon_{0_u} \end{array}
%\right|\right.
%\left.
%\begin{array}{c} \bar{\varepsilon}_1 \\
%\bar{\varepsilon}_{0_1}  \end{array}  ; \begin{array}{c} \Lambda \\
%\lambda \end{array}
%\right\rangle \nn \right|^2,
%\end{align}
%and where
where 
\begin{align}
\delta_u &= (-1)^{|I|} \prod_{k\in I,k\neq u} \left({\alpha_0}_u - {\alpha_0}_k -
(-1)^{(k)}\right)^{-1}\prod_{k\in\tilde{I}} \left(\alpha_k - {\alpha_0}_u \right),\ \ u\in I',
\end{align}
are the reduced matrix elements.
Note that ${\rho}_{ru}$ in equation (\ref{RhoExp}) is non-vanishing only when $r\in \tilde{I}$ and $u\in I'$.

Substituting the expressions for ${c}_r$ and ${\delta}_u$ into equation 
 (\ref{RhoExp}) initially gives
\begin{align*}
{\rho}_{ru} &= ({\alpha}_r-{\alpha_0}_u + 1)^{-1}({\alpha}_r-{\alpha_0}_u)^{-1} \prod_{k\in \tilde{I},k\neq r} \left(\alpha_r - \alpha_k \right)^{-1}\prod_{k\in
I} \left(\alpha_r - {\alpha_0}_k - (-1)^{(k)}\right() \\
& ~\times (-1)^{|I|} \prod_{k\in I,k\neq u} \left({\alpha_0}_u - {\alpha_0}_k -
(-1)^{(k)}\right)^{-1}\prod_{k\in\tilde{I}} \left(\alpha_k - {\alpha_0}_u \right),\ \ r\in \tilde{I},u\in I' 
\end{align*}
Now $({\alpha}_r-{\alpha_0}_u)^{-1}$ will cancel the corresponding term from $\delta_u$ while $
({\alpha}_r-{\alpha_0}_u + 1)^{-1}$ will only cancel a term in $c_r$ when $u$ is odd. We therefore have
\begin{align*}
{\rho}_{ru} &= ({\alpha}_r-{\alpha_0}_u + 1)^{-1}\prod_{k\in \tilde{I},k\neq r} \left(\alpha_r - \alpha_k \right)^{-1}\prod_{k\in
I} \left(\alpha_r - {\alpha_0}_k - (-1)^{(k)}\right) \\
& ~\times (-1)^{|I|} \prod_{k\in I,k\neq u} \left({\alpha_0}_u - {\alpha_0}_k -
(-1)^{(k)}\right)^{-1}\prod_{k\in\tilde{I},k \neq r} \left(\alpha_k - {\alpha_0}_u \right),\ \ r\in \tilde{I},u\in I' 
\end{align*}
for $u$ even and
\begin{align*}
{\rho}_{ru} &= (-1)^{|I|} \prod_{k\in \tilde{I},k\neq r} 
\left(
\frac 
{\alpha_k - {\alpha_0}_u  }
{\alpha_r - \alpha_k }
\right)
\prod_{k\in I,k \neq u} 
\left(
\frac
{ \alpha_r - {\alpha_0}_k - (-1)^{(k)} }
{{\alpha_0}_u - {\alpha_0}_k - (-1)^{(k)} }
\right)
,\ \ r\in \tilde{I},u\in I_1
\end{align*}
for $u$ odd.
Note that the expression for $\rho_{ru}$ always evaluates to a positive value as expected.

\section{Reduced Wigner coefficients} 
\label{Wigner}

{\bf Remark 1:} 
It is important to note that within the $gl(m|n)$ projection operator expressions we may have $\alpha_r = \alpha_k$ for some $r \neq k$. This is related to the occurrence of atypical irreducible representations in the tensor product
of $V({\varepsilon_1})\otimes V(\Lambda)$ or $V({\varepsilon_1})^*\otimes V(\Lambda)$. The
set of $\Lambda$ for which this happens, however, is closed in the Zariski topology
\cite{Hump1972} on $H^*$. It follows that the roots of the characteristic identity are distinct on an open and hence dense subset of
$H^*$. Hence without loss of generality, we will make the assumption that the roots are distinct. Furthermore, the invariants derived in this paper are given by rational
polynomial functions which are continuous in the Zariski topology. 

{\bf Remark 2:} 
When applying the projection operators we must take care to distinguish between type 1 unitary and type 2 unitary modules. These classes of modules are defined as follows. Consider the positive-definite, invariant, sesquilinear form defined on an irreducible highest weight module $V(\lambda)$ of $gl(m|n)$ 
$$
\langle a_{pq} | w \rangle = (-1)^{\epsilon [(p) + (q)]} \langle v | a_{qp} w \rangle , \epsilon  \in \{0,1\}.
$$
When $\epsilon = 0$ we call $V(\Lambda)$ a type 1 unitary irrep while for $\epsilon = 1$ we call $V(\Lambda)$ a type 2 unitary irrep. The induced form on a tensor product space $V(\Lambda) \otimes V(\mu)$ is non-degenerate only when restricted to a direct summand of the tensor product space and only when $ V(\Lambda)$ and $V(\mu)$ are of the same type. This induced form is necessarily unique by Schur's lemma. We then define Wigner coefficients with respect to this form. 

Due to these considerations we now consider the type 1 unitary and type 2 unitary cases of Wigner coefficients seperately.

Let $e_i$ denote the Gelfand-Tsetlin (GT) basis states for the (type 1 unitary) vector module $V(\varepsilon_1)$ and ${e^\Lambda_\beta}$ denote the (GT) basis states for the irreducible type 1 unitary module $V(\Lambda)$ of highest weight $\Lambda$. Then the matrix elements of $\bar{P}[r]$ can be given in the form
\begin{align}
\left\langle e^\Lambda_\beta | \bar{P}[r]^j_i | e^{\Lambda}_\alpha \right\rangle =
\sum_\gamma \left\langle e^\Lambda_\beta \otimes e_i | e^{\Lambda + \varepsilon_r}_\gamma \right\rangle
\left\langle e^{\Lambda+\varepsilon_r}_\gamma | e_j \otimes e^\Lambda_\alpha \right\rangle, \label{BarPij}
\end{align}
where
$$
\left\langle e^{\Lambda+\varepsilon_r}_\gamma | e_j \otimes e^\Lambda_\alpha \right\rangle,
$$
are the vector (fundamental) Wigner coefficients.

From Schur's lemma we observe that the fundamental WCs factorize as follows
\begin{align}
\left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_k\\ \lambda+\varepsilon_{0_r} \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
e_i\otimes \begin{array}{c} \Lambda \\ \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle &= 
\left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_k\\ \lambda+\varepsilon_{0_r} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \varepsilon_1 \\ \varepsilon_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle 
\left\langle\left. 
\begin{array}{c} \lambda+\varepsilon_{0_r} \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
e_i\otimes \begin{array}{c} \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle,\label{Schur1}\\ 
1 < i < m+n, \nn
\end{align}
where $1 < k \leq m+n$,~$1 < r \leq m+n-1$, 
$\Lambda$ denotes the type 1 unitary highest weight of $gl(m|n)$, $\lambda$ denotes the highest weight of $gl(m|n-1)$ and $[\Lambda_0]$ denotes the GT pattern of the $gl(m|n-2)$ subalgebra. In addition, the first term on the rhs of equation (\ref{Schur1}) is a reduced Wigner coeficient (RWC) which is independent of the highest
weight labels of $[\Lambda_0]$ and $[\Lambda'_0]$.

Setting $i=m+n$ gives
\begin{align}
\left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_k\\ \lambda \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
e_{m+n} \otimes \begin{array}{c} \Lambda \\ \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle = \delta_{[\Lambda'_0][\Lambda]}
 \left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_k\\ \lambda \end{array}
\right|\right.
\left.
\begin{array}{c} 
\varepsilon_1 \\ \dot{0}
\end{array}
;
\begin{array}{c} \Lambda \\ 
\lambda \end{array}
\right\rangle  , \label{WCBraKet1}
\end{align}
where the RWC on the rhs reduces to the WC in this case which are independent of $[\Lambda_0]$ and $[\Lambda'_0]$ as expected. 
The WC in equation (\ref{WCBraKet1}) is given by the eigenvalues of the invariant
$$ 
\bar{c}_r = \bar{P}[r]_{m+n}^{\ m+n}
$$
since from equation (\ref{BarPij}) we have
\begin{align}
\bar{c}_r  &= \left| \left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_r\\ \lambda \end{array}
\right|\right.
\left.
\begin{array}{c} \varepsilon_1 \\
\dot{0} \end{array} 
;
 \begin{array}{c} \Lambda \\
\lambda \end{array}
\right\rangle \right|^2. \label{WigCoefCBar}
\end{align}

We therefore see that the matrix elements of the projection $\bar{P}[r]_{m+n}^{\ m+n}$ determine
the squares of the fundamental Wigner coefficients and depend only on the top two rows of the corresponding Gelfand-Tsetlin basis states.

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
~~\\
We now turn to the dual fundamental Wigner coefficients and proceed similarly. 
Denoting $\bar{e}_i$ to be the Gelfand-Tsetlin (GT) basis states of the (type 2 unitary) dual vector module and ${e^\Lambda_\beta}$ to be the (GT) basis states for the irreducible type 2 unitary module $V(\Lambda)$ of highest weight $\Lambda$ we have 
\begin{align}
\left\langle e^\Lambda_\beta | P[r]^j_i | e^{\Lambda}_\alpha \right\rangle =
\sum_\gamma \left\langle e^\Lambda_\beta \otimes \bar{e}_i | e^{\Lambda - \varepsilon_r}_\gamma \right\rangle
\left\langle e^{\Lambda-\varepsilon_r}_\gamma | \bar{e}_j \otimes e^\Lambda_\alpha \right\rangle, \label{Pij}
\end{align}
where
$$
\left\langle e^{\Lambda-\varepsilon_r}_\gamma | \bar{e}_j \otimes e^\Lambda_\alpha \right\rangle,
$$
are the dual fundamental Wigner coefficients. The above quantities may be expressed in terms of the $gl(m|n)$ highest weight labels of $\Lambda$ and the highest weight labels of the $gl(m|n-1)$ subalgebra.

Let $\bar{\varepsilon}_k$ denote the weights of the $gl(m|n)$ contravariant vector irrep. These weights are given by $\bar{\varepsilon}_k = -\varepsilon_{m+n+1-k} (1 \leq k \leq m+n)$. We similarly define the $gl(m|n-1)$ fundamental weights $\bar{\varepsilon}_{0_r} =
\varepsilon_{0_{m+n-r}} = (1 \leq r \leq m+n-1) $.

Again, from Schur's lemma we observe that the dual fundamental WCs factorize as follows
\begin{align}
\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_k\\ \lambda-\varepsilon_{0_r} \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
\bar{e}_i\otimes \begin{array}{c} \Lambda \\ \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle &= 
\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_k\\ \lambda-\varepsilon_{0_r} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \bar{\varepsilon}_1 \\ \bar{\varepsilon}_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle 
\left\langle\left. 
\begin{array}{c} \lambda-\varepsilon_{0_r} \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
\bar{e}_i\otimes \begin{array}{c} \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle,\label{Schur2}\\
~~\nn\\
1 < i < m+n, \nn
\end{align}
where $1 < k \leq m+n$,~$1 < r \leq m+n-1$, 
$\Lambda$ denotes the type 2 unitary highest weight of $gl(m|n)$, $\lambda$ denotes the highest weight of $gl(m|n-1)$ and $[\Lambda_0]$ denotes the GT pattern of the $gl(m|n-2)$ subalgebra. As in the vector Wigner coefficient case, the first term on the rhs of equation (\ref{Schur2}) is a reduced Wigner coeficient (RWC) which is independent of the highest
weight labels of $[\Lambda_0]$ and $[\Lambda'_0]$.

Setting $i=m+n$ gives
\begin{align}
\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_k\\ \lambda \\ {[\Lambda'_0]} \end{array}
\right|\right.
\left.
\bar{e}_{m+n} \otimes \begin{array}{c} \Lambda \\ \lambda \\
{[\Lambda_0]} \end{array}
\right\rangle = \delta_{[\Lambda'_0][\Lambda]}
 \left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_k\\ \lambda \end{array}
\right|\right.
\left.
\begin{array}{c} 
\bar{\varepsilon}_1 \\ \dot{0}
\end{array}
;
\begin{array}{c} \Lambda \\
\lambda \end{array}
\right\rangle  , \label{WCBraKet2}
\end{align}
where the RWC on the rhs reduces to the WC in this case which are independent of $[\Lambda_0]$ and $[\Lambda'_0]$ as expected. 
The WC in equation (\ref{WCBraKet2}) is given by the eigenvalues of the invariant
$$ 
c_r = P[r]_{\ m+n}^{m+n}
$$
since from equation (\ref{Pij}) we have
\begin{align}
c_r &= \left| \left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_r\\ \lambda \end{array}
\right|\right.
\left.
\begin{array}{c} \bar{\varepsilon}_1 \\
\dot{0} \end{array}  ; \begin{array}{c} \Lambda \\
\lambda \end{array}
\right\rangle \right|^2. \label{WigCoefCUnbar}
\end{align}
As in the vector fundamental Wigner case we see that the matrix elements of the projection  $P[r]_{\ m+n}^{m+n}$ determine
the squares of the dual fundamental Wigner coefficients and depend only on the top two rows of the corresponding Gelfand-Tsetlin basis states.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Summary}
The expressions for the WCs of equations (\ref{WCBraKet1}) and (\ref{WCBraKet2}) together with the RWCs of equations (\ref{Schur1}) and (\ref{Schur2}) including their phases \cite{GIW2,GIW3} are then given by
\begin{align}
& \left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_r\\ \lambda
 \end{array}
\right|\right.
\left.
\begin{array}{c} \varepsilon_1 \\ 0 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle = \left[ \prod_{k\in \tilde{I}',k\neq r} \left(\bar{\alpha}_r - \bar{\alpha}_k\right)^{-1}\prod_{k\in
I'} \left(\bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)}\right) \right]^{1/2}
,\ \ r\in \tilde{I}'
\end{align}

\begin{align}
&\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_r\\ \lambda
 \end{array}
\right|\right.
\left.
\begin{array}{c} \bar{\varepsilon}_1 \\ 0 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle
= \left[ \prod_{k\in \tilde{I},k\neq r} \left(\alpha_r - \alpha_k \right)^{-1}\prod_{k\in
I} \left(\alpha_r - {\alpha_0}_k - (-1)^{(k)}\right) \right]^{1/2}
,\ \ r\in \tilde{I} .
\end{align}



\begin{align}
& \left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_r\\ \lambda+\varepsilon_{0_u} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \varepsilon_1 \\ \varepsilon_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle = (-1)^{(r)(u)} S(r-u) \nn\\
&~~\times 
\left[ 
\frac{
(-1)^{|I'|} \prod_{k\in\tilde{I'},k \neq r} \left(\bar{\alpha}_k - \bar{\alpha_0}_u \right)
\prod_{k\in I'} \left(\bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)}\right) 
}
{
(\bar{\alpha}_r-\bar{\alpha_0}_u + 1)
\prod_{k\in \tilde{I'},k\neq r} \left(\bar{\alpha}_r - \bar{\alpha}_k \right)
\prod_{k\in I',k\neq u} \left(\bar{\alpha_0}_u - \bar{\alpha_0}_k - (-1)^{(k)}\right)
}
\right]^{1/2}
, \ \ r\in \tilde{I'},u\in I   \label{FinalBarredEven}
\end{align}


\begin{align}
& \left\langle\left. 
\begin{array}{c} \Lambda+\varepsilon_r\\ \lambda+\varepsilon_{0_u} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \varepsilon_1 \\ \varepsilon_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle = (-1)^{(r)(u)} S(r-u) \nn\\
&~~\times \left[ (-1)^{|I'|} \prod_{k\in \tilde{I'},k\neq r} 
\left(
\frac 
{\bar{\alpha}_k - \bar{\alpha_0}_u  }
{\bar{\alpha}_r - \bar{\alpha}_k }
\right)
\prod_{k\in I',k \neq u} 
\left(
\frac
{ \bar{\alpha}_r - \bar{\alpha_0}_k - (-1)^{(k)} }
{\bar{\alpha_0}_u - \bar{\alpha_0}_k - (-1)^{(k)} }
\right)
\right]^{1/2}
,\ \ r\in \tilde{I'},u\in I_1 \label{FinalBarredOdd}
\end{align}

\begin{align}
&\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_r\\ \lambda-\varepsilon_{0_u} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \bar{\varepsilon}_1 \\ \bar{\varepsilon}_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle
= (-1)^{(r)(u) +(r) + (u)} S(r-u)
\nn \\
&~~\times
\left[
\frac{
(-1)^{|I|}
\prod_{k\in I} \left(\alpha_r - {\alpha_0}_k - (-1)^{(k)}\right)
\prod_{k\in\tilde{I},k \neq r} \left(\alpha_k - {\alpha_0}_u \right)
}
{
({\alpha}_r-{\alpha}_u + 1)
\prod_{k\in \tilde{I},k\neq r} \left(\alpha_r - \alpha_k \right)
\prod_{k\in I,k\neq u} \left({\alpha_0}_u - {\alpha_0}_k - (-1)^{(k)}\right)
} 
\right]^{1/2}
,\ \ r\in \tilde{I},u\in I' \label{FinalUnBarredEven}
\end{align}

\begin{align}
&\left\langle\left. 
\begin{array}{c} \Lambda-\varepsilon_r\\ \lambda-\varepsilon_{0_u} 
 \end{array}
\right|\right.
\left.
\begin{array}{c} \bar{\varepsilon}_1 \\ \bar{\varepsilon}_{0_1} 
 \end{array}
; \begin{array}{c} \Lambda \\ \lambda
 \end{array}
\right\rangle = (-1)^{(r)(u) +(r) + (u)} S(r-u) 
\nn\\
&~~\times
\left[
 (-1)^{|I|} \prod_{k\in \tilde{I},k\neq r} 
\left(
\frac 
{\alpha_k - {\alpha_0}_u  }
{\alpha_r - \alpha_k }
\right)
\prod_{k\in I,k \neq u} 
\left(
\frac
{ \alpha_r - {\alpha_0}_k - (-1)^{(k)} }
{{\alpha_0}_u - {\alpha_0}_k - (-1)^{(k)} }
\right)
\right]^{1/2}
,\ \ r\in \tilde{I},u\in I_1  \label{FinalUnBarredOdd}
\end{align}
where the positive square root is always taken, odd indices are considered greater than even indices, 
$$
S(x) = sgn(x),~~S(0)=1.
$$
and where we recall

\begin{align*}
{\bar{\alpha_0}}_i &= i - 1 -\Lambda_i  , &1\leq i\leq m-1, \\
{\bar{\alpha_0}}_\mu &= \Lambda_\mu + m + 1 - \mu  ,  &1\leq \mu \leq n-1 , \\ 
{\alpha_0}_i &= \Lambda_i + m - n + 1 - i  , &1\leq i\leq m-1, \\
{\alpha_0}_\mu &= \mu - \Lambda_\mu -n + 1, &1\leq \mu \leq n-1 , \\
\bar{\alpha}_i  &= i - 1 -{\tilde{\Lambda}}_i , &1\leq i\leq m, \\
\bar{\alpha}_\mu &= {\tilde{\Lambda}}_\mu + m + 1 - \mu,  &1\leq \mu \leq n , \\
\alpha_i &= {\tilde{\Lambda}}_i + m - n - i, &1\leq i\leq m, \\
\alpha_\mu &= \mu-{\tilde{\Lambda}}_\mu - n, &1\leq \mu \leq n .  
\end{align*}
Note that the $gl(m|n)$ roots $\alpha$ and $\bar{\alpha}$ are related to the $gl(m|n-1)$ roots $\alpha_0$ and $\bar{\alpha}_0$ by the substitution $n \rightarrow n - 1$.

{\bf Final remark...}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%Substituting the expressions for $\bar{c}_r$ and $\bar{\delta}_u$ into equation 
% (\ref{RhoBarExp}) initially gives
%\begin{align*}
% \bar{\rho}_{ru} &= (-1)^{|I'|} (\bar{\beta}_r-\bar{\alpha}_u +
%1)^{-1}(\bar{\beta}_r-\bar{\alpha}_u)^{-1} \prod_{k\in \tilde{I}',k\neq r} \left(\bar{\beta}_r - \bar{\beta}_k\right)^{-1}\prod_{k\in
%I'} \left(\bar{\beta}_r - \bar{\alpha}_k - (-1)^{(k)}\right) \\
%& ~\times \prod_{k\in I',k\neq u}\left(\bar{\alpha}_u - \bar{\alpha}_s -
%(-1)^{(s)}\right)^{-1} \prod_{k\in \tilde{I}'}\left(\bar{\beta}_k - \bar{\alpha}_u \right) 
%\end{align*}
%so
%\begin{align*}
% \bar{\rho}_{ru} &= (-1)^{|I'|} (\bar{\beta}_r-\bar{\alpha}_u +
%1)^{-1}\prod_{k\in \tilde{I}',k\neq r} \left(\bar{\beta}_r - \bar{\beta}_k\right)^{-1}\prod_{k\in
%I'} \left(\bar{\beta}_r - \bar{\alpha}_k - (-1)^{(k)}\right) \\
%& ~\times \prod_{k\in I',k\neq u}\left(\bar{\alpha}_u - \bar{\alpha}_k -
%(-1)^{(k)}\right)^{-1} \prod_{k\in \tilde{I}', k \neq r}\left(\bar{\beta}_k - \bar{\alpha}_u \right) 
%\end{align*}
%Now for $(u)=1$ there will be a corresponding term in
%$$
%\prod_{k\in
%I'} \left(\bar{\beta}_r - \bar{\alpha}_k - (-1)^{(k)}\right)
%$$
%that matches
%$$
%(\bar{\beta}_r-\bar{\alpha}_u +
%1)^{-1}.
%$$
%For $(u)=0$ 
%
%%For $(r) = 0$ and $(u) = 0$ we note that $r \in \bar{I}_0$ and $u \in I_0$ so directly we have $r \neq u$.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
%\section{Summary of main results} 
%\label{resultsum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Acknowledgements
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section*{Acknowledgments}
%
This work was supported by the Australian Research Council through Discovery Project
DP140101492. 
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  References
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\newpage
\section*{Appendix A: Symmetry relations}
$$
\psi: V_0 \otimes V(\Lambda) \rightarrow V, ~~ \psi(e_i \otimes \nu) = \psi^i \nu, ~~\forall \nu \in V(\Lambda)
$$
~~\\
$$
V = \oplus V'(\Lambda + \epsilon_r)
$$
~~
\begin{align*}
\left\langle e_\beta^{\Lambda  + \epsilon_r} | \psi^i | e^{\Lambda}_\alpha \right\rangle 
= \left \langle \Lambda + \epsilon_r || \psi || \Lambda \right \rangle
\left\langle e^{\Lambda+\epsilon_r}_\beta | e_i \otimes e^{\Lambda}_\alpha \right\rangle
\end{align*}
~~
$$
\phi_i = (\psi^j)^\dagger
$$
~~
\begin{align*}
\left\langle e_\beta^{\Lambda  - \epsilon_r} | \phi^i | e^{\Lambda}_\alpha \right\rangle 
= \left \langle \Lambda - \epsilon_r || \phi || \Lambda \right \rangle
\left\langle e^{\Lambda-\epsilon_r}_\beta | \bar{e}_i \otimes e^{\Lambda}_\alpha \right\rangle
\end{align*}
which implies
~~
\begin{align*}
&\left \langle \Lambda + \epsilon_r || \psi || \Lambda \right \rangle
\left\langle e^{\Lambda+\epsilon_r}_\beta | e_i \otimes e^{\Lambda}_\alpha \right\rangle \\
&~~= \left\langle e_\beta^{\Lambda  + \epsilon_r} | \psi^i | e^{\Lambda}_\alpha \right\rangle \\
&~~= \left\langle e_\alpha^{\Lambda} | \phi^i | e^{\Lambda + \epsilon_r}_\beta \right\rangle^*\\
&~~=\left \langle \Lambda || \phi || \Lambda + \epsilon_r \right \rangle^*
\left\langle e^{\Lambda}_\alpha | \bar{e}_i \otimes e^{\Lambda+\epsilon_r}_\beta \right\rangle.
\end{align*}
~~
We therefore have the symmetry condition
$$
\left\langle e^{\Lambda+\epsilon_r}_\beta | e_i \otimes e^{\Lambda}_\alpha \right\rangle
= \eta \left\langle e^{\Lambda}_\alpha | \bar{e}_i \otimes e^{\Lambda+\epsilon_r}_\beta \right\rangle^*
$$
where $\eta$ is a constant that is independent of $i, \alpha$ and $\beta$ and is given by
$$
\left \langle \Lambda + \epsilon_r || \psi || \Lambda \right \rangle \eta = \left \langle \Lambda || \phi || \Lambda + \epsilon_r \right \rangle^*.
$$
To determine $\eta$ we ...
~~\\
~~\\
$$
\eta = \prod^{m+n}_{k=1} 
\left( 
\frac
{\alpha_a - \alpha_k - (-1)^{(k)}}
{\alpha_a - \alpha_k}
\right)
$$




\newpage
\begin{thebibliography}{10}

%\bibitem{ZhaGou1990} M.D. Gould and R.B. Zhang, J. Math. Phys. {\bf 31} (1990) 2552.
%
%\bibitem{GouZha1990} M.D. Gould and R.B. Zhang, Lett. Math. Phys. {\bf 20} (1990) 221.
%
%\bibitem{SNR1977} M. Scheunert, W. Nahm and V. Rittenberg, J. Math. Phys. {\bf 18} (1977) 146. 
% 
\bibitem{GIW1} M.D. Gould, P.S. Isaac and J.L. Werry, J. Math. Phys. {\bf 54} (2013), 013505.
% 
\bibitem{GIW2} M.D. Gould, P.S. Isaac and J.L. Werry, J. Math. Phys. {\bf 55} (2014), 011703.
%
\bibitem{GIW3} J.L. Werry, M.D. Gould and P.S. Isaac, J. Math. Phys. {\bf 56} (2015), 121703.
% 
%\bibitem{Green1971} H.S. Green, J. Math. Phys. {\bf 12} (1971) 2106.
%%  
%\bibitem{BraGre1971} A.J. Bracken and H.S. Green, J. Math. Phys. {\bf 12} (1971) 2099.
%%  
%% \bibitem{Green1975} H.S. Green, J. Austral. Math. Soc. Ser. B {\bf 19} (1975) 129.
%% 
%\bibitem{OBCantCar1977} D.M. O'Brien, A. Cant and A.L. Carey, Ann. Inst. Henri 
%Poincar\'e, Section A: Physique th\'eorique {\bf 26} (1977) 405.
%  
%\bibitem{Gould1985} M.D. Gould, J. Austral. Math. Soc. Ser. B {\bf 26}  (1985) 257.
%
%\bibitem{JarGre1979} P.D. Jarvis and H.S. Green, J. Math. Phys.  {\bf 20}  (1979) 2115.
% 
%\bibitem{GreJar1983}  H.S. Green and P.D. Jarvis, J. Math. Phys.  {\bf 24}  (1983) 1681.
%  
%\bibitem{Gould1987}  M.D. Gould, J. Austral. Math. Soc. Ser. B {\bf 28}  (1987) 310.
%  
\bibitem{GT1950}
I.M. Gelfand and M.L. Tsetlin, Dokl. Akad. Nauk., SSSR {\bf 71} (1950) 825 (Russian).
English translation in: I.M. Gelfand, ``Collected Papers'', Vol II, Berlin:
Springer-Verlag (1988) 653.
  
\bibitem{GT1950b}
I.M. Gelfand and M.L. Tsetlin, Dokl. Akad. Nauk., SSSR {\bf 71} (1950) 1017 (Russian).
English translation in: I.M. Gelfand, ``Collected Papers'', Vol II, Berlin:
Springer-Verlag (1988) 657.
  
\bibitem{BB1963} G.E. Baird and L.C. Biedenharn, J. Math. Phys. {\bf 4} (1963) 1449.
%  
% \bibitem{Palev1987} T. D. Palev, Funct. Anal. Appl. {\bf 21} (1987) 245.
%  
% \bibitem{Palev1989} T. D. Palev, Funct. Anal. Appl. {\bf 23} (1989) 141.
% 
\bibitem{StoiVan2010} N.I. Stoilova and J. Van der Jeugt, J. Math. Phys. {\bf 51} (2010) 093523.
% 
\bibitem{Hump1972} J.E. Humphreys, Introduction to Lie algebras and representation theory, volume 9 of Graduate Texts in Mathematics. Springer, New York, 1972.


% \bibitem{Molev2011} A.I. Molev, Bull. Inst. Math. Acad. Sinica {\bf 6} (2011) 415.
% 
% \bibitem{TolIstSmi1986} V.N. Tolstoy, I.F. Istomina and Yu.F. Smirnov, in ``Group
% Theoretical Methods in Physics: Proceedings of the Third Yurmala Seminar'', Yurmala, USSR,
% 1985, Ed. M.A. Markov, V.I. Man'ko and V.V. Dodonov, VNU Science Press, Utrecht (1986)
% 337.
%%  
%\bibitem{Kac1977} V.G. Kac, Adv. in Math. {\bf 26} (1977) 8.
%% 
%\bibitem{Kac1978} V.G. Kac, Lecture Notes in Math. {\bf 676}, Springer, Berlin (1978) 597.
%% 
%\bibitem{NahmSch1976} W. Nahm and M. Scheunert, J. Math. Phys. {\bf 17} (1976) 868.
%% 
%\bibitem{GouZha19902} M.D. Gould and R.B. Zhang, J. Math. Phys. {\bf 31} (1990) 1524.
%% 
%\bibitem{GouBraHug1989} M.D. Gould, A.J. Bracken and J.W.B. Hughes, J. Phys. A: Math. Gen.
%{\bf 22} (1989) 2879.
% 
%\bibitem{GouJarBra1990} M.D. Gould, P.D. Jarvis and A.J. Bracken, J. Math. Phys. {\bf 31}
%(1990) 2803. 
%% 
%% \bibitem{PaStVa1994} T.D. Palev, N.I. Stoilova and J. Van der Jeugt, Comm. Math. Phys.
%% {\bf 166} (1994) 367.
%% 
%\bibitem{Gould1992}
%M.D. Gould, J. Math. Phys. {\bf 33} (1992) 1023.
%% 
\bibitem{Gould1981} M.D. Gould, J. Math. Phys. {\bf 22} (1981) 15.

% \bibitem{SchNaRit1976} M. Scheunert, W. Nahm and V. Rittenberg, J. Math. Phys. {\bf 17}
% (1976) 1626.
% 
% \bibitem{Sch1979} M. Scheunert, Lecture Notes in Math. {\bf 716}, Springer, Berlin (1979).
% 
% \bibitem{Ram1971} P. Ramond, Phys. Rev. D {\bf 3} (1971) 2415.
% 
% \bibitem{NevSchw1971} A. Neveu and J.H. Schwarz, Nucl. Phys. B {\bf 31} (1971) 86.
% 
% \bibitem{VolAk1973} D.V. Volkov and V.P. Akulov, Phys. Lett. B {\bf 46} (1973) 109.
% 
% \bibitem{WessZum1974} J. Wess and B. Zumino, Nucl. Phys. B {\bf 70} (1974) 39.
% 
% \bibitem{SalStrath1974} A. Salam and J. Strathdee, Nucl. Phys. B {\bf 76} (1974) 477.
% 
% \bibitem{Scherk1975} J. Scherk, Rev. Mod. Phys. {\bf 47} (1975) 123.
% 
% \bibitem{FayFer1977} P. Fayat and S. Ferrara, Phys. Rep. {\bf 32} (1977) 249.
% 
% \bibitem{CorNeSt1975} L. Corwin, Y. Ne'eman and S. Sternberg, Rev. Mod. Phys. {\bf 47}
% (1975) 573.
% 
% \bibitem{Musson2012} I.M. Musson, Graduate Studies in Math. {\bf 131}, AMS (2012).
% 
% \bibitem{BeiStau2003} N. Beisert and M. Staudacher, Nucl. Phys. B {\bf 670} (2003) 439.
% 
% \bibitem{Mina2012} J.A. Minahan, Lett. Math. Phys. {\bf 99} (2012) 33.
% 
% \bibitem{GalMar2004} W. Galleas and M.J. Martins, Nucl. Phys. B {\bf 699} (2004) 455.
% 
% \bibitem{EssFraSal2005} F.H.L. Essler, H. Frahm and H. Saleur, Nucl. Phys. B {\bf 712}
% (2005) 513.
% 
% \bibitem{ZhYaZh2006} S.Y. Zhao, W.L. Yang and Y.Z. Zhang, Commun. Math. Phys. {\bf 268}
% (2006) 505.
% 
% \bibitem{RagSat2007} E. Ragoucy and G. Satta, JHEP09 (2007) 001.
% 
% \bibitem{FraMar2011} H. Frahm and M.J. Martins, Nucl. Phys. B {\bf 847} [FS] (2011) 220.
% 
% \bibitem{SchomSal2006} V. Schomerus and H. Saleur, Nucl. Phys. B {\bf 734} [FS] (2006) 221.
% 
% \bibitem{Ridout2009} D. Ridout, Nucl. Phys. B {\bf 810} [FS] (2009) 503.
% 
% \bibitem{StoiVan2008} N.I. Stoilova and J. Van der Jeugt, J. Phys. A: Math. Theor. {\bf
% 41} (2008) 075202.
% 
% \bibitem{LievStoiVan2008} S. Lievens, N.I. Stoilova and J. Van der Jeugt, Commun. Math.
% Phys. {\bf 281} (2008) 805.
% 
% 
% \bibitem{Molev2006} A.I. Molev, Handbook of Algebra {\bf 4} (2006) 109.
 
% 
% \bibitem{KamKyPal1989} A.H. Kamupingene, N.A. Ky, T.D. Palev, J. Math. Phys. {\bf 30}
% (1989) 553.
% 
% 
% \bibitem{PalStoi1990} T.D. Palev, N.I. Stoilova, J. Math. Phys. {\bf 31} (1990) 953.
% 
% 
% \bibitem{Dirac1936} P.A.M. Dirac, Proc. R. Soc. Lond. A {\bf 155} (1936) 447.
% 
% \bibitem{BB1964b} G.E. Baird and L.C. Biedenharn, J. Math. Phys. {\bf 5} (1964) 1723.
% 
\bibitem{Gould1978} M.D. Gould, J. Austral. Math. Soc. Ser. B {\bf 20}  (1978) 401.
% 
\bibitem{Gould1980} M.D. Gould, J. Math. Phys. {\bf 21} (1980) 444.
% 
% 
\bibitem{Gould1981b} M.D. Gould, J. Math. Phys. {\bf 22} (1981) 2376.
% 
% \bibitem{Gould1984} M.D. Gould, J. Phys. A: Math. Gen. {\bf 17} (1984) 1.
% 
% \bibitem{Kostant1975} B. Kostant, J. Func. Anal {\bf 20} (1975) 257.
% 
% \bibitem{Hannabuss1997} K. Hannabuss, ``An Introduction to Quantum Theory'', Oxford
% University Press, Oxford (1997).
% 
% \bibitem{BB1964} G.E. Baird and L.C. Biedenharn, J. Math. Phys. {\bf 5} (1964) 1730.
% 
% \bibitem{LouBei1970} J.D. Louck and L.C. Biedenharn, J. Math. Phys. {\bf 11} (1970) 2368.
% 
% \bibitem{ZhGoBr1991} R.B. Zhang, M.D. Gould and A.J. Bracken, Nucl. Phys. B {\bf 354}
% (1991) 625.
% 
% \bibitem{RitSch1992} V. Rittenberg and M. Scheunert, J. Math. Phys. {\bf 33} (1992) 436.
% 
% \bibitem{Mozr2005} M. Mozrzymas, Int. J. Geom. Meth. Mod. Phys. {\bf 2} (2003) 393.
% 
% \bibitem{PaisRitt1975} A. Pais and V. Rittenberg, J. Math. Phys. {\bf 16} (1975) 2062.
% 
% \bibitem{Mezin1977} L. Mezincescu, J. Math. Phys. {\bf 18} (1977) 453.
% 
% \bibitem{Mozr2004} M. Mozrzymas, J. Phys. A: Math. Gen. {\bf 37} (2004) 9515.
% 
% \bibitem{JarMur1983} P.D. Jarvis and M.K. Murray, J. Math. Phys. {\bf 24} (1983) 1705.
% 
% \bibitem{JaRuYa2011}
% P.D. Jarvis, G. Rudolph and L.A. Yates, J. Phys. A: Math. Theor. {\bf 44} (2011) 235205.

\end{thebibliography}


\end{document}
